Sperm do not evolve to collaborate in female meiotic drive.

### 2014-05-09 writeup_and_notes/male_dependent_drive.tex
edited polymorphic figure

\begin{figure}
\includegraphics[width = 0.8 \textwidth]{Figures/effect_of_dominance_on_invasion_space_one_graph.eps} 
\caption{Invasion analysis of an allele whose effect
 on female meoisis is mediated by the genotype of the fertilizing
 male. The area below the solid/dotted line is the parameter region
 where the allele can invade/fix (from $1/1000$ and $999/1000$
 \gc{maybe should lower this}). Note
 that all of the fixation lines are on top of each other as dominance
 parameter makes little difference here. The allele will be
 polymorphic in the parameter space where the solid (invasion) line
 falls above the dotted (fixation) line. Note that this is a very
 narrow parameter range, and only exists if the allele has a
 reasonable degree on dominance}  \label{Effect_of_dominance}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width = 0.8 \textwidth]{../Scripts/effect_of_dominance_on_invasion_space_four_graph.eps} 
\caption{Invasion analysis of an allele whose effect
 on female meoisis is mediated by the genotype of the fertilizing
 male.  As above wee assume a heterozygous female will transmit the $B$ allele 
  with probabilities  $\frac{1}{2}$,  $\frac{1}{2} + h(d-\frac{1}{2}) $ or $d$, 
 if she mated with a n $AA$, $AB$, or $BB$ male,  respectively.  The allele suffers a recessive fitness cost $s$.  
 The four panels correspond to different dominance relationships.
In the parameter space below the invasion (solid) line the self promotor
 driver can invade. In the parameter space below the fixation (long
 dash) line the self promotor can fix in the population. In the last
 two panels the invasion line is above the fixation line and so the
 allele can be maintained as a polymorphism in that thin slice of
 parameter space between the two lines. These results were 
  obtained using the recursion. In the final panel we show the
  fixation line (small dashes) as predicted by our HWE approximation.
}  \label{Effect_of_dominance}
\end{figure}
